Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis

### 2018-03-21 paper/finalish/article.tex
use sensible identifiers for the figures

\begin{figure}
\centering
\includegraphics[width=.9\linewidth]{Figures/attr_all.pdf}
\caption{Posterior mean attribution ($F$) of human cases with 80\% credible intervals for source: poultry (red), ruminants (blue), water (green) and others (purple) over the rurality scales from highly rural area to main urban areas. The attribution is generated from both the linear and the categorical models, given the sampling distribution of genotypes with evolutionary information (the asymmetric Island model) or without any genetic information (the Dirichlet model).}
\label{fig2}
\end{figure}

@@

Posterior attribution of human cases of campylobacteriosis ($F$) with 80\% credible intervals for each source are illustrated for each rurality grade in Figure~\ref{fig2}. The graphs are categorized by the type of genetic model (asymmetric Island or Dirichlet) and the manner in which the rurality variable is modelled (categorical or linear on the logit scale).

>>>>

\begin{figure}
\centering
\includegraphics[width=.9\linewidth]{Figures/attr_all.pdf}
\caption{Posterior mean attribution ($F$) of human cases with 80\% credible intervals for source: poultry (red), ruminants (blue), water (green) and others (purple) over the rurality scales from highly rural area to main urban areas. The attribution is generated from both the linear and the categorical models, given the sampling distribution of genotypes with evolutionary information (the asymmetric Island model) or without any genetic information (the Dirichlet model).}
\label{fig:attribution}
\end{figure}

@@

Posterior attribution of human cases of campylobacteriosis ($F$) with 80\% credible intervals for each source are illustrated for each rurality grade in Figure~\ref{fig:attribution}. The graphs are categorized by the type of genetic model (asymmetric Island or Dirichlet) and the manner in which the rurality variable is modelled (categorical or linear on the logit scale).
